The Transport Mechanisms of Polar Solutes in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2018-12-03 Ben_Manuscripts/transport/Outline.tex
Minor updates

@@

  \subsection{Simulated Estimates of Macroscopic Diffusion Coefficients}\label{section:D_macro}

@@

@@

  In order to truly understand the molecular origins of the macroscopic diffusion
  coefficients in Section~\ref{section:D_macro}, we studied the microscopic interactions
  between solutes and the membrane that lead to the observed dwell and hop distributions.

@@

  Even in the center of the pore, where the density of water molecules is 
  highest, individual water molecules still exhibit hop diffusion as they
  create a tight hydrogen bond network.

@@

@@

  The hydroxyl functional group of alcohol molecules is a hydrogen bond donor
  and prefers to donate it's hydrogen to strongly polarized carboxylate head
  groups.

  As alcohol groups increase in hydrophobic character, they are more inclined
  to stick to the outside edges of the pore. 
  \begin{itemize}
	\item The alkane tails prefer to stay at the edges of the pore. 
	\item They tend to get trapped between monomers and closer to 
	the tail region. 
	\item The entrapment is further stabilized by hydrogen bonds with
	ether oxygens connecting the monomer's alkane tails to the head groups.
  \end{itemize}

@@

  The hydrophobic character of the two methyl groups on acetone causes the methyl
  groups to gravitate towards the outside of the pore, while the carbonyl group
  reaches towards the pore center in order to

@@

  \subsection{Experimental comparison of diffusion results}

@@

  We calculated the macroscopic diffusion coefficients of each solute as 
  approximated by a CTRW model.

@@

  We have validated our results using experimental DOSY NMR measurements.

>>>>

  \subsubsection*{Radial Distribution Functions}

  We measured the average radial distance of each solute of interest from the pore
  centers.
  \begin{itemize}
	\item We binned the radial distances and then normalized by the volume
	of the annulus defined by the bin edges.
	\item Although the pores are often described as straight, they have a
	small degree of tortuosity which disrupts the RDF calcuation 
	\item We obtain the best RDF by constructing splines that run through the
	pore centers.
	\item We construct the splines by dividing the membrane into 20 slices
	in the $z$-direction. Within each slice, we calculate the location of 
	the pore centers based on the average location of the aromatic rings
	that make up the monomer head groups.
	\item When calculating the RDF, the radial distance from the pore center
	is based on the distance between the solute center-of-mass and the ($x$, $y$)
	coordinates of appropriate point on the spline.
  \end{itemize}

@@

  \subsection{Macroscopoic Diffusion Coefficients}

  \subsection{Simulated Predictions}\label{section:D_macro}

@@

  \subsection{Experimental Measurements}

@@

  In order to truly understand the molecular origins of the macroscopic
  diffusion coefficients in Section~\ref{section:D_macro}, we studied the
  microscopic interactions between solutes and the membrane that lead to the
  observed dwell time and hop distributions.
  \begin{itemize}
	\item We studied the radial distribution functions of solutes as a
	function of distance from the pore center
	\item We looked at hydrogen bonding patterns
	\item Order parameters
  \end{itemize}

  The radial distribution function of each solute studied is shown in 
  Figure TBD.

@@

  Even in the center of the pore, where the density of water molecules is
  highest, individual water molecules exhibit hop diffusion as they create a
  tight hydrogen bond network.
  %TODO: the following is a hypothesis
  \begin{itemize}
	\item Water sticks to pore walls
	\item Dwell times are short
	\item Water tumbles across pore for a while until it sticks again. 
	\item Water gets caught in h-bonds with other water molecules away
	from pore center.
  \end{itemize}

@@

  %TODO: study diffusion mechanism of water

@@

  The hydroxyl functional group of alcohol molecules is a hydrogen bond donor
  and prefers to donate it's hydrogen to more strongly polarized carboxylate head
  groups.

  As alcohol groups increase in hydrophobic character, they are more inclined
  to stick to the outside edges of the pore. 
  \begin{itemize}
	\item The alkane tails prefer to stay at the edges of the pore.
	\item Radial distribution functions show peaks at pore edges, however
	smaller alcohols have high densities near the pore center. 
	\item They tend to get trapped between monomers and closer to 
	the tail region. 
	\item The entrapment is further stabilized by hydrogen bonds with
	ether oxygens connecting the monomer's alkane tails to the head groups.
	%TODO: quantify h-bonds with ether oxygens and carbonyl oxygens
  \end{itemize}

@@

  The hydrophobic character of the two methyl groups on acetone causes the methyl
  groups to gravitate towards the outside of the pore, while the carbonyl group
  reaches towards the pore center in order to hydrogen bond with water molecules.
  \begin{itemize}
	\item Order parameter defined between vector along carbonyl and vector extending
	from acetone COM to pore center is non-zero.
  \end{itemize}

@@

@@

  We calculated the macroscopic diffusion coefficients of each solute as 
  approximated by a CTRW model and validated our estimates using experimental
  DOSY NMR measurements.

@@

  We showed that hydrogen bonding between solutes and Na-GA3C11 monomers plays
  a major role in mechanism by which molecules traverse the nanopores.
